Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-05-30 performance_comparison.tex
[MM] some words on the results

In addition to the baseline value $\bar{\bP}_0$, two alternative values are considered: $\bP_0 = 4\bar{\bP}_0$ and $\bP_0 = \frac{1}{4}\bar{\bP}_0$. These correspond, respectively, to doubling and halving the initial uncertainty associated with the state vector, as it's possible to verify from \eqref{eq:sigma_from_P}.

\begin{figure}
	\centering
	\includegraphics{Fig/gamma_sensitivity.pdf}
	\hfill
	\includegraphics{Fig/Pzero_sensitivity.pdf}
	\caption{Effect of $\ga^\textrm{TLC}$ (left panel) and $P_0$ (right panel) on optimal trajectory. The parameter $\ga^\textrm{TLC}$ span in the range $\left[0,3\right]$ corresponding to a probability to meet the track limit constraint of 50\% and 99\%, respectively. In the left panel, in addition to the baseline value $\bar{\bP}_0$ (black line), two alternative values are considered: $\bP_0 = 4\bar{\bP}_0$ (blue line) and $\bP_0 = \frac{1}{4}\bar{\bP}_0$ (red line). These correspond, respectively, to doubling and halving the initial uncertainty associated with the state vector.}
	\label{fig:ol_sensitivities}
\end{figure}

>>>>

In addition to the baseline value $\bar{\bP}_0$, two alternative values are considered: $\bP_0 = 4\bar{\bP}_0$ and $\bP_0 = \frac{1}{4}\bar{\bP}_0$. These correspond, respectively, to doubling and halving the initial uncertainty associated with the state vector, as it's possible to verify from \eqref{eq:sigma_from_P}. 
For simplicity, a diagonal $\bar{\bP}_0$ has been chosen for this study. In this case, $\bar{\bP}_0$ is constructed by assigning the standard deviations of the elements of the state vector---collected in the vector $\bar{\boldsymbol{\sigma}}_0$---and placing their squared values along the diagonal. 
The values of $\bar{\boldsymbol{\sigma}}_0$ has been chosen accordingly to the range of variation of the associated variable. In particular, assuming the state vector is ordered as described in Section~\ref{sec:vehicle_model}, we selected $\bar{\boldsymbol{\sigma}}_0 = \left[0.1\,\textrm{m/s}, 0.01\,\textrm{m/s}, 0.01\,\textrm{rad/s}, 1\,\textrm{m}, 1\,\textrm{m}, 0.0175\,\textrm{rad}\right]^T$.

The results of the analysis conducted on this parameter are shown in the right panel of Figure~\ref{fig:ol_sensitivities} where the black line corresponds to the baseline, obtained setting $\bP_0 = \bar{\bP}_0$, while the red and the blue lines corresponds to configurations with $\bP_0 = \frac{1}{4}\bar{\bP}_0$ and $\bP_0 = 4\bar{\bP}_0$, respectively. 
Obviously, using a larger initial covariance matrix results in a greater covariance matrix after $H$ steps, which in turn leads to a higher back-off term. This is reflected in the blue line, which travels closer to the centerline w.r.t. the other two lines.
\begin{figure}
	\centering
	\includegraphics{Fig/gamma_sensitivity.pdf}
	\hfill
	\includegraphics{Fig/Pzero_sensitivity.pdf}
	\caption{Effect of $\ga^\textrm{TLC}$ (left panel) and $P_0$ (right panel) on optimal trajectory. The parameter $\ga^\textrm{TLC}$ span in the range $\left[0,3\right]$ corresponding to a probability to meet the track limit constraint of 50\% and 99\%, respectively. In the left panel, in addition to the baseline value $\bar{\bP}_0$ (black line), two alternative values are considered: $\bP_0 = 4\bar{\bP}_0$ (blue line) and $\bP_0 = \frac{1}{4}\bar{\bP}_0$ (red line). These correspond, respectively, to doubling and halving the initial uncertainty associated with the state vector.}
	\label{fig:ol_sensitivities}
\end{figure}
